Modal Verification Patterns for Systems Software

### 2025-09-13 paper.tex
updates for administrativia for camera-ready

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/2018/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

@@

%\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
 \usepackage{proof}
\usepackage{array}
\usepackage{iris}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}
% Useful macros from Isaac Oscar Gariano: a very simple library for author-specific change notations:
%  After calling \newAuthor{<name>}{<colour>}
% You can use \<name>{<text>} to add a comment
% Or \<name>A{<text>} to  write stuff in your colour (to denote additional text)
% Or \<name>B{<text>} is similar, but changes the background (to highlight stuff?)
% I may add more commands later
% (there's a 'changes' package with similar functionality, but it has a habit of breaking when you use it with  the Define environment)
\newcommand\newAuthor[2]{%
        \ExpandArgs{c}\newcommand{#1}[1]{\todo[color=#2!10, bordercolor=#2, inline]{\textbf{#1:}~##1}}
	\ExpandArgs{c}\newcommand{#1A}[1]{\textcolor{#2}{##1}}
        \ExpandArgs{c}\newcommand{#1B}[1]{\colorbox{#2!30}{\textcolor{black}{##1}}}}
\newtheorem*{remark}{Remark}
\newcommand{\loc}{\textsf{Loc}}
\newcommand{\sepimp}{\mathrel{-\mkern-6mu*}}
\newcommand{\blackdiamond}{\rotatebox[origin=c]{45}{$\vcenter{\hbox{$\scriptscriptstyle\blacksquare$}}$}}

\newAuthor{Ismail}{blue}
\newAuthor{Colin}{cyan}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>00000000.0000000.0000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%
%%%
%%% Keywords. The author(s) should pick words that accurately describe
%%% the work being presented. Separate the keywords with commas.
%\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for, Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

>>>>

% %% Rights management information.  This information is sent to you
% %% when you complete the rights form.  These commands have SAMPLE
% %% values in them; it is your responsibility as an author to replace
% %% the commands and values with those provided to you when you
% %% complete the rights form.
% \setcopyright{acmlicensed}
% \copyrightyear{2018}
% \acmYear{2018}
% \acmDOI{XXXXXXX.XXXXXXX}
% %% These commands are for a PROCEEDINGS abstract or paper.
% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%   conference title from your rights confirmation email}{June 03--05,
%   2018}{Woodstock, NY}
% %%
% %%  Uncomment \acmBooktitle if the title of the proceedings is different
% %%  from ``Proceedings of ...''!
% %%
% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
% %%  June 03--05, 2018, Woodstock, NY}
% \acmISBN{978-1-4503-XXXX-X/2018/06}
\acmYear{2025}
\copyrightyear{2025}
\setcopyright{cc}
\setcctype[4.0]{by}
\acmConference[PLOS '25]{13th Workshop on Programming Languages and Operating Systems}{October 13--16, 2025}{Seoul, Republic of Korea}
\acmBooktitle{13th Workshop on Programming Languages and Operating Systems (PLOS '25), October 13--16, 2025, Seoul, Republic of Korea}
\acmDOI{10.1145/3764860.3768337}
%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

@@

%\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
 \usepackage{proof}
\usepackage{array}
\usepackage{iris}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}
% Useful macros from Isaac Oscar Gariano: a very simple library for author-specific change notations:
%  After calling \newAuthor{<name>}{<colour>}
% You can use \<name>{<text>} to add a comment
% Or \<name>A{<text>} to  write stuff in your colour (to denote additional text)
% Or \<name>B{<text>} is similar, but changes the background (to highlight stuff?)
% I may add more commands later
% (there's a 'changes' package with similar functionality, but it has a habit of breaking when you use it with  the Define environment)
% \newcommand\newAuthor[2]{%
%         \ExpandArgs{c}\newcommand{#1}[1]{\todo[color=#2!10, bordercolor=#2, inline]{\textbf{#1:}~##1}}
% 	\ExpandArgs{c}\newcommand{#1A}[1]{\textcolor{#2}{##1}}
%         \ExpandArgs{c}\newcommand{#1B}[1]{\colorbox{#2!30}{\textcolor{black}{##1}}}}
% \newtheorem*{remark}{Remark}
\newcommand{\loc}{\textsf{Loc}}
\newcommand{\sepimp}{\mathrel{-\mkern-6mu*}}
\newcommand{\blackdiamond}{\rotatebox[origin=c]{45}{$\vcenter{\hbox{$\scriptscriptstyle\blacksquare$}}$}}

% \newAuthor{Ismail}{blue}
% \newAuthor{Colin}{cyan}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Kuru and Gordon}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003790.10003793</concept_id>
<concept_desc>Theory of computation~Modal and temporal logics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003790.10002990</concept_id>
<concept_desc>Theory of computation~Logic and verification</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010941.10010949</concept_id>
<concept_desc>Software and its engineering~Operating systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Modal and temporal logics}
\ccsdesc[500]{Theory of computation~Logic and verification}
\ccsdesc[500]{Software and its engineering~Operating systems}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>00000000.0000000.0000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>00000000.00000000.00000000</concept_id>
%  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
%
%%%
%%% Keywords. The author(s) should pick words that accurately describe
%%% the work being presented. Separate the keywords with commas.
\keywords{separation logic, modal logic, verification, operating systems}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}
